### 2020-11-13 Thesis-Chapter5-ThreatModel.tex
Finish STRIDE threats

\begin{figure}[p!]
  \centering\CaptionFontSize
  \includegraphics[width=\linewidth]{dfds/build/DAR-level-1-crypto-iphone-LDAMSR-setup.png}
  \caption{The LDAWMSR maintenance data flow diagram.}
  \label{fig-dfd-ldawmsr-setup}
\end{figure}

@@

The proposal has been illustrated. What threats does it introduce? Recall from \mysec{sec-crypto-basics} that security
can be expressed in the properties of authentication, integrity, non-repudiation, confidentiality, availability, and
authorization. Threats are often expressed as the negative of these properties: spoofing, tampering, repudiation,
information disclosure, denial of service, and elevation of privileged \cite{shostack_threat_2014}. This section
analyzes \ldawmsr using these categories. Threats that fit under multiple categories, such as tampering for the effect
of repudiation, are listed only once.

To save space, the tables use shorthand for law enforcement (LE); law enforcement officer (LEO); law enforcement agency
(LEA); Device ID (DID);

@@

\threattablebegin{Spoofing}{spoofing}{Spoof}
  S1 & Device is spoofed to LE via plant
  & Attackers plant a device to get LE to unlock it for them.
  & Require the device to be in the forensics department itself the entire time it is unlocked.
  \\ \hline
  S2 & Device is spoofed to LE via forged DID
  & Attackers rig a device to report a different DID and record the entered unlock artifacts, allowing them into a
    target device.
  & Add a hardware integrity check or alternatively unlock the device in a Faraday cage, extract its data, and destroy
    it.
  \\ \hline
  S3 & LEO is spoofed to LEA
  & Attackers pose as a LEO while the LEA relays back unlock artifacts.
  & Require the device to be in the forensics department itself the entire time it is unlocked.
  \\ \hline
  S4 & LEA is spoofed to vendor during key exchange
  & Attackers pose as an LEA in order to spoof future access requests.
  & Vendor key exchange process involves thorough in-person verification.
  \\ \hline
  S5 & LEA is spoofed to vendor during access request
  & Attackers pose as a LEA and submit an access request. Requires forged legal documents and a stolen LEA private key
    (unless attacker is an insider or has executed a spoofed key exchange).
  & Vendor independently verifies all legal documents. Vendor supports a key revocation and update process that involves
    the same level of in-person verification.
  \\ \hline
  S6 & Manufacturer is spoofed to vendor
  & Attackers pose as the manufacturer to inject malicious data into the DID-Seal database. Must be combined with other
    attacks to be of use.
  & Vendor authenticates data transfers between manufacturing and corporate (does not address a compromised manufacturer
    network or an inside threat).
\threattableend

@@

Tampering threats are listed in \mytab{table-tampering}.

\threattablebegin{Tampering}{tampering}{Tamper}
  T1 & Defensive user corrupts DSK, DID, or token
  & LE attempts at perform \ac{EA} will fail due to corrupt data. Requires compromise of the Secure Enclave or advanced
    hardware manipulation tools.
  & Since these values are known at manufacturing time and never change, they can be made read-only. (The symmetric key
    variant of \ldawmsr requires updating the symmetric equivalent of the public DSK, and is therefore more vulnerable
    to this threat.)
  \\ \hline
  T2 & Defensive user destroys the \ac{EA} hardware interface
  & LE attempts at perform \ac{EA} will fail due to damaged hardware.
  & Manufacture the device to require destructive disassembly to access the interface. This increases the cost
    associated with deploying and using the system.
  \\ \hline
  T3 & LE insider tampers with DID before digital signature
  & LEA receives an unauthorized device's unlock artifacts. Can be combined with other attacks to compromise a device.
  & Randomize DID's to make them unguessable, meaning a target device must be in possession in order for the attacker to
    know what DID to use. Input to the vendor's \ac{HSM} could also include data from the legal documents, such as
    device S/N; the \ac{HSM} would hash the value and verify a match before returning the unlock artifacts.
  \\ \hline
  T4 & Attacker tampers with hardware transparency mechanism
  & The device user is unaware that the device was unlocked. Highly implementation dependent, but certainly requires
    advanced hardware manipulation tools.
  & Manufacture the device to require destructive disassembly to access the interface.
\threattableend

@@

\threattablebegin{Repudiation}{repudiation}{Repudiation}
  R1 & Attacker or authoritarian government repudiates unlock attempt
  & The user is unaware that someone tried to access their device.
  & Manufacture the device to require destructive disassembly to access the interface, or use the same hardware
    transparency mechanism to mark mere access attempts as well.
  \\ \hline
  R2 & Authoritarian government repudiates demanding vendor assistance
  & Governments not respecting the legal framework governing the system can bully the vendor and try to force access
    while maintaining deniability.
  & This is close to being an out of scope threat under the ``rule of law'' exception. However, one could design the
    system to require requests to be recorded on a public ledger. This opens up several new difficulties.
  \\ \hline
  R3 & LEA repudiates having unlocked a device
  & The device is undeniably unlocked, but the LEA claims it was not them, allowing possible violations of civil
    liberties and harming transparency.
  & ...
  \\ \hline
  R4 & Vendor repudiates having responded to an access request
  & The device is undeniably unlocked, but the vendor claims they did not provide the unlock artifacts, allowing the
    vendor to cover up leaks or unsavory policy decisions by suggesting the device was instead hacked. Harms
    transparency.
  & ...
\threattableend

@@

Information disclosure threats are listed in \mytab{table-disclosure}.

\threattablebegin{Information Disclosure}{disclosure}{Information \\ Disclosed}
  I1 & .
  & .
  & .
  \\ \hline
  I2 & .
  & .
  & .
\threattableend

@@

Denial of service threats are listed in \mytab{table-dos}.

\threattablebegin{Denial of Service}{dos}{Service Denied}
  D1 & .
  & .
  & .
  \\ \hline
  D2 & .
  & .
  & .
\threattableend

@@

Elevation of privilege are listed in \mytab{table-privilege}.

\threattablebegin{Elevation of Privilege}{privilege}{Privilege Gained}
  E1 & .
  & .
  & .
  \\ \hline
  E2 & .
  & .
  & .
\threattableend

>>>>

\begin{figure}[H]
  \centering\CaptionFontSize
  \includegraphics[width=\linewidth]{dfds/build/DAR-level-1-crypto-iphone-LDAMSR-setup.png}
  \caption{The LDAWMSR maintenance data flow diagram.}
  \label{fig-dfd-ldawmsr-setup}
\end{figure}

@@

The proposal has been illustrated. What threats does it introduce? Recall from \mysec{sec-crypto-basics} that security
can be expressed in the properties of authentication, integrity, non-repudiation, confidentiality, availability, and
authorization. Threats are often expressed as the negative of these properties: spoofing, tampering, repudiation,
information disclosure, \acl{DOS}, and elevation of privileged \cite{shostack_threat_2014}. This section
analyzes \ldawmsr using these categories. Threats that fit under multiple categories, such as tampering for the effect
of repudiation, are listed only once.

To save space, the tables use shorthand for law enforcement (LE), law enforcement officer (LEO), law enforcement agency
(LEA), Device ID (DID), Device Seal Key (DSK), \acf{DOS}

@@

\threattablebegin{Spoofing}{spoofing}{Spoof}
  S1 & Device is spoofed to LE via plant
  & Attackers plant a device to get LE to unlock it for them.
  & Require the device to be in the forensics department itself the entire time it is unlocked.
  \\ \hline
  S2 & Device is spoofed to LE via forged DID
  & Attackers rig a device to report a different DID and record the entered unlock artifacts, allowing them into a
    target device.
  & Add a hardware integrity check or alternatively unlock the device in a Faraday cage (to prevent telemetry), extract
    its data, and destroy it (to prevent recovering stored data).
  \\ \hline
  S3 & LEO is spoofed to LEA
  & Attackers pose as a LEO while the LEA relays back unlock artifacts.
  & Require the device to be in the forensics department itself the entire time it is unlocked.
  \\ \hline
  S4 & LEA is spoofed to vendor during key exchange
  & Attackers pose as an LEA in order to spoof future access requests.
  & Vendor key exchange process involves thorough in-person verification.
  \\ \hline
  S5 & LEA is spoofed to vendor during access request
  & Attackers pose as a LEA and submit an access request. Requires forged legal documents and a stolen LEA private key
    (unless attacker is an insider or has executed a spoofed key exchange).
  & Vendor independently verifies all legal documents. Vendor supports a key revocation and update process that involves
    the same level of in-person verification.
  \\ \hline
  S6 & Manufacturer is spoofed to vendor
  & Attackers pose as the manufacturer to inject malicious data into the DID-DSK database. Must be combined with other
    attacks to be of use.
  & Vendor authenticates data transfers between manufacturing and corporate (does not address a compromised manufacturer
    network or an inside threat).
\threattableend

@@

Tampering threats are listed in \mytab{table-tampering}. \ii{S2} relies on tampering similar to \ii{T1}.

\threattablebegin{Tampering}{tampering}{Tamper}
  T1 & Defensive user corrupts DSK, DID, or token
  & LE attempts at perform \ac{EA} will fail due to corrupt data. Requires compromise of the Secure Enclave or advanced
    hardware manipulation tools.
  & Since these values are known at manufacturing time and never change, they can be made read-only. (The symmetric key
    variant of \ldawmsr requires updating the symmetric equivalent of the public DSK, and is therefore more vulnerable
    to this threat.)
  \\ \hline
  T2 & Defensive user destroys the \ac{EA} hardware interface
  & LE attempts to perform \ac{EA} will fail due to damaged hardware.
  & Manufacture the device to require destructive disassembly to access the interface. This increases the cost
    associated with deploying and using the system.
  \\ \hline
  T3 & LE insider tampers with DID before digital signature
  & LEA receives an unauthorized device's unlock artifacts. Can be combined with other attacks to compromise a device.
  & Randomize DID's to make them unguessable, meaning a target device must be in possession in order for the attacker to
    know what DID to use. Input to the vendor's \ac{HSM} could also include data from the legal documents, such as
    device S/N; the \ac{HSM} would hash the value and verify a match before returning the unlock artifacts.
  \\ \hline
  T4 & Attacker tampers with hardware transparency mechanism
  & The device user is unaware that the device was unlocked. Highly implementation dependent, but certainly requires
    advanced hardware manipulation tools.
  & Manufacture the device to require destructive disassembly to access the interface.
\threattableend

@@

\threattablebegin{Repudiation}{repudiation}{Repudiation}
  R1 & Attacker or authoritarian government repudiates unlock attempt
  & The user is unaware that someone tried to access their device.
  & Manufacture the device to require destructive disassembly to access the interface, or use the same hardware
    transparency mechanism to mark mere access attempts as well.
  \\ \hline
  R2 & Authoritarian government repudiates demanding vendor assistance
  & Governments not respecting the legal framework governing the system can bully the vendor and try to force access
    while maintaining deniability.
  & This is close to being an out of scope threat under the ``rule of law'' exception. However, one could design the
    system to require requests to be recorded on a public ledger. This opens up several new difficulties.
  \\ \hline
  R3 & LEA repudiates having unlocked a device
  & The device is undeniably unlocked, but the LEA claims it was not them, allowing possible violations of civil
    liberties and harming transparency.
  & The escrow agent could require some identifying information before unlocking, such as the LEA's public key digitally
    signed by the vendor.
  \\ \hline
  R4 & Vendor repudiates having responded to an access request
  & The device is undeniably unlocked, but the vendor claims they did not provide the unlock artifacts, allowing the
    vendor to cover up leaks or unsavory policy decisions by suggesting the device was instead hacked. Harms
    transparency.
  & The same identifying information used in \ii{R3} would implicate the vendor (assuming the integrity of the vendor's
    signing key).
\threattableend

@@

Information disclosure threats are listed in \mytab{table-disclosure}. In addition to the threats listed here, all
attacks aimed at gaining unauthorized access to a device constitute information disclosure threats. Most spoofing
attacks are aimed at disclosing information intended for another party.

\threattablebegin{Information Disclosure}{disclosure}{Information \\ Disclosed}
  I1 & Attacker exposes the DSK, DID, the encrypted class key, or hashed token
  & By design, none of the information stored on the phone is sensitive. The most consequential information that could
    be stolen is the DID, which could be paired with other attacks. Disclosing the DID requires either disassembly and
    time vaulting or advanced hardware inspection tooling.
  & Sensitivity of this data has already been mitigated as much as possible.
  \\ \hline
  I2 & Attacker intercepts unlock artifacts between LEA \ac{HSM} and device
  & The attacker is able to unlock the target device alone. Must be combined with a spoofed DID to be of use to other
    devices (see \ii{S2}). The could record the values to replay them after the phone has been returned.
  & See \ii{S2}. If choosing not to destroy the device, to prevent replay attacks, a new token could be generated and
    stored in the vendor HSM, with the new hash installed during the unlock process.
  \\ \hline
  I3 & Attacker steals the LEA private key
  & The attacker is now able to spoof the LEA and decrypt returned unlock artifacts. Without the devices (which are
    already in LE possession), the artifacts are not useful. See \ii{S4} and \ii{S5} for LEA spoofing attacks.
  & The key is stored in an \ac{HSM}, which has extensive security measures. See \ii{S5} for a revocation and update
    mitigation.
  \\ \hline
  I4 & Attacker steals the DID-DSK database
  & This is the big prize, the largest source of centralized risk. With the database, attackers could directly
    compromise (or more likely, sell access to) any mobile device using this system in their possession, after
    disassembly, and after the time vault.
  & \ii{R3} defines a mitigation that requires use of a vendor private key to create a digital signature as part of the
    authentication process. If used, that key would have to be compromised as well for the database to be of use.
    However, if the database is compromised, that key probably is too. Savage argues that \ac{HSM}s, though imperfect,
    actually do provide very strong assurance. Responses could be rate-limited, and leaking an entire database once it's
    in the \ac{HSM} could not go unnoticed. Getting the data in may be harder---see \ii{I5}.
  \\ \hline
  I5 & Attacker steals device unlock artifacts between manufacturing and vendor \ac{HSM}
  & Intercepting the unlock artifacts at the source achieves the same effect as \ii{I4}, only the data set is not
    complete. Instead of granting the ability to unlock any device, including a specific target, this is suited for
    getting access down the line or for sale.
  & The unlock artifacts generation process must be treated as sensitively as the \ac{HSM} itself. The artifacts should
    be encrypted immediately and periodically transported to the corporate \ac{HSM} on physical media. This threat is
    difficult to definitively mitigate.
\threattableend

@@

\Ac{DOS} threats are listed in \mytab{table-dos}. In addition to the threats listed, \ii{S4} can be used for \ac{DOS} by
surreptitiously invalidating a LEA's identity key, and \ii{T1} and \ii{T2} are tampering attacks designed to deny LEAs
from using the \ac{EA} mechanism.

\threattablebegin{Denial of Service}{dos}{Service Denied}
  D1 & Unlock artifacts recovery
  & \ii{S6} could be used to inject corrupt data to the DID-DSK database, potentially overwriting actual unlock artifact
    data.
  & Verify integrity of new data before entering it into the database, and disallow overwriting entirely.
\threattableend

@@

Elevation of privilege are listed in \mytab{table-privilege}. Spoofing to usurp a entity's privilege or using any attack
to unlock a device without authorization can be seen as escalation of privilege.

\threattablebegin{Elevation of Privilege}{privilege}{Privilege Gained}
  E1 & Foreign intelligence or organized crime recruits an insider
  & The primary attacker gains inside access through coercion or bribery, making any other attack easier.
  & Limit the employees, accounts, and computers involved in any element of the system. Perform background checks on
    each employee and maintain detailed logs.
  \\ \hline
  E2 & Unexposed hardware interface allows access to Secure Enclave
  & The attacker gains access to Secure Enclave operations and data, undermining the device and achieving unlock without
    following the \ac{EA} protocol.
  & The time vaulting protocol and all communication over the interface must be thoroughly tested, and if possible,
    formally proven to be logically sound. Analysis must include side channel attacks to affect the time vaulting or
    leak internal data.
\threattableend

\section{Risk Analysis}

How much risk does \ldawmsr introduce? The answer varies based on how many mitigations are implemented. If the device is
required to be unlocked on LEA premises and destructive disassembly is chosen, several threats are significantly
reduced. The irreducible risks are those posed by the DID-DSK database and the Secure Enclave itself.
